\begin{acknowledgements}

Chris, thank you for this opportunity. Your thoughts are the contours of this thesis, and your foresight has continually put me in the right place at the right time.

Jamie, thank you for answering every naive question and for the kindness and care with which you spoon-fed me achievable tasks as I inched towards consciousness. Andrew, thank you for always being one step ahead of me and so graciously showing me the way. Brian, thank you for all the times you happily entertained whatever ultra-specific issue I happened to be facing.

Juliette, thank you for everything, most of all the teamwork, the guidance, and being so unrelentingly reliable. It's strange to think that our day-to-day professional lives will diverge soon; I look forward to when they cross again.

Everyone in MTest, thank you for the immediate and effortless companionship and teamwork. Corrinne, thank you for the advice, perspective, and care. Susan, thank you for constantly working side by side. Andre, thank you for saving me when I dropped that tiny screw. Thank you all for all the sleepless nights and pushing so hard towards our common goal. Lorenzo, thank you for the all-day-every-day support, the laughter, and the constant willingness to explain.

PRB 3000, the first two years of grad school would have broken me if not for our shenanigans. Thank you for being my family, dragging me through core classes, and helping me feel ok as an imposter. Jovan, your coffee fueled each day and knowing you were on the other side of the Walhalla helped make Clintonville feel like home.

Paul Bloom and David Horner, thank you for showing me physics, for putting up with me every time I insisted on making things harder than they had to be, and for giving me a second chance. Stuart Wick, thank you for introducing me to Minutemen and infinite-dimensional function spaces. Bob Stanek, thank you for showing me experimental particle physics and for always having my back.

Dad, Julie, Bob, Ann, Jerry, Patrizia, Mark, Jeanne, and all my family, thank you for the unconditional support and love I've felt all my life. Thank you for looking at the world with me and always wanting to talk about cool stuff. I am in a position to write this thesis because of your examples, efforts, and care.

Cristiana and Montague, you are on every page. Thank you for sharing this adventure with me.

\end{acknowledgements}