\section{Background estimation}
\label{bg}
\fxnote{add intro blurb?}
\subsection{Background sources}
\label{bg_sources}
The vast majority of leptons from SM processes are prompt. There are, however, a few notable processes that produce leptons with large \ad values that may pass the preselection: (1) leptons from prompt decays whose \ad is poorly measured (``mismeasurements"), (2) leptons from  decays of tau leptons (``taus"), and (3) leptons from decays of B or D mesons (``heavy flavor"). Note that the leptons from these processes generally do not share a common displaced vertex. We perform several cross checks to ensure that processes in which leptons share a common displaced vertex do not contribute significantly in the signal regions (SRs). Section~\ref{additional_bg_checks} presents several additional studies that confirm that the SR contributions of leptons from material interactions, cosmic rays, and SM hadrons are either negligible or already accounted for by the background estimation procedure outlined in Section~\ref{abcd}.

The \ad distributions of leptons from the three main background sources vary according to lepton flavor and parent particle. Tau leptons, B mesons, and D mesons have proper decay lengths of \SI{87}{\um}, approximately \SI{500}{\um}, and approximately \linebreak[4]\SI{100}{\um}, respectively, so leptons from taus will generally be less displaced than leptons from heavy flavor. Furthermore, mismeasurements are more common for electrons than for muons due to the superior muon $d_0$ resolution. Figure~\ref{ttbar_d0_behavior}, which shows the relative contribution of each source of leptons as a function of \ad in simulated \ttbar events that pass the \Pe\Pgm\ channel preselection, shows how mismeasurements dominate at all \ad values for electrons while taus and heavy flavor contribute meaningfully for muons with $\ad\gtrsim\SI{100}{\um}$.

\input{figures/bg/ttbar_d0_behavior}

In addition to the \ad behavior of individual leptons, we are also interested in understanding whether any background processes introduce correlation in \ad between pairs of leptons. Having confirmed that the obvious potential source of \ad-\ad correlation, i.e. pairs of leptons that share a common displaced vertex, do not contribute meaningfully to the SR, we next investigate possible sources of correlation from mismeasurements, taus, and heavy flavor. As the preselection criteria ensure that we are operating in the regime in which lepton \ad resolution does not depend meaningfully on \pt or $\eta$, and because the two candidate leptons in a given event are nearly always from prompt processes and/or independent decays, mismeasurements generally will not introduce \ad-\ad correlation.

Taus and heavy flavor, on the other hand, could potentially introduce \ad-\ad correlation through correlation in parentage between the two candidate leptons. As will be shown in Section~\ref{cr_closure_tests}, we find that taus lead to exactly this type of correlation through processes such as \ztautaull while heavy flavor does not. Figure~\ref{dy_d0_behavior} shows the fraction of muons from different SM parents as a function of \ad in simulated Drell-Yan events that pass the \Pgm\Pgm\ preselection with the added requirement that both muons come from the same type of parent particle. Here, we see the same characteristic \ad behavior of leptons from taus and also that the isolation criteria effectively eliminates events in which both leptons come from a heavy-flavor meson. We therefore conclude that while leptons from mismeasurements, taus, and heavy flavor will all contribute in the SR, only leptons from taus will introduce meaningful \ad-\ad correlation. Furthermore, the characteristic \ad behavior of leptons from taus seen in Figs.~\ref{ttbar_d0_behavior} and \ref{dy_d0_behavior} implies that this correlation will specifically impact the \num{100} to \SI{500}{\um} region.

\input{figures/bg/dy_d0_behavior}

\subsection{Data-driven ABCD method}
\label{abcd}
We estimate the SR background yields with a data-driven method in which the lepton \ad distributions serve as composite models of all background processes. Specifically, we employ an ABCD method using the \ad of two leptons. We label the two \ad values in each channel as \ada and \adb, which correspond to the leading electron and leading muon in the \Pe\Pgm\ channel, the leading and subleading electrons in the \Pe\Pe\ channel, and the leading and subleading muons in the \Pgm\Pgm\ channel. As a first step, we categorize the events that pass the preselection criteria into four regions (A, B, C, and D) of the \ada-\adb plane, as shown in Fig.~\ref{abcd_regions}.

\input{figures/bg/abcd_regions}

In order to maximize sensitivity to a wide range of new particle lifetimes, we subdivide region D into four SRs:
\begin{itemize}
    \itemsep0em
    \item SR I:   $\num{100}\leq\ada<\SI{500}{\um}$, $\num{100} < \adb<\SI{500}{\um}$
    \item SR II:  $\num{100}\leq\ada<\SI{500}{\um}$, $\SI{500}{\um}<\adb<\SI{10}{\cm}$
    \item SR III: $\SI{500}{\um} \leq \ada<\SI{10}{\cm}$, $\num{100} < \adb<\SI{500}{\um}$
    \item SR IV:  $\SI{500}{\um} \leq \ada<\SI{10}{\cm}$, $\SI{500}{\um}<\adb<\SI{10}{\cm}$
\end{itemize}
The exact boundaries between the four SRs are motivated by the expected contributions of the different background sources, as explained in \ref{bg_sources}. This approach also necessitates that the definitions of regions B and C vary in accordance with the SR for which a given estimate is performed (e.g. only the events in the $\num{100}\leq\ada<\SI{500}{\um}$ range of region B are considered when estimating the yields of SR I and II). Finally, we subdivide SR I into two bins using one lepton's \pt to further increase sensitivity to high-mass, low-lifetime new physics. Table~\ref{pt_bins} lists the \pt boundary in each channel and year.

\input{tables/pt_bins}

We then use the number of events in regions A, B, and C to estimate the expected background in each SR. The basic estimation procedure depends on the assumption that \ada and \adb are uncorrelated. If this assumption holds, then $N_{\text{B}}/N_{\text{A}}=N_{\text{D}}/N_{\text{C}}$ and the number of background events in D is equal to $N_{\text{B}}\times N_{\text{C}}/N_{\text{A}}$, where $N_{\text{X}}$ is the number of background events in the given region. We find that \ada and \adb are indeed uncorrelated over much of the \ad-\ad plane, but the correlation discussed in Section~\ref{bg_sources} renders the simple ABCD method insufficient to estimate the background in SR I. After quantifying the degree of correlation in Section~\ref{cr_closure_tests}, we define a procedure to correct the simple SR I ABCD estimate in Section~\ref{abcd_correction}.

When performing the background estimate and closure tests, we treat the 2016 data and simulation separately from the 2017--2018 data and simulation to avoid any correlations between \ada and \adb that may arise from the differences between the original and Phase-1 pixel detectors employed by CMS in 2016 and 2017--2018, respectively (see Section~\ref{tracker}).

\subsection{Closure tests in control regions}
\label{cr_closure_tests}
We perform several closure tests of the background estimation procedure in data and simulation to test the method and quantify the degree of \ada-\adb correlation from the processes discussed in \ref{bg_sources}. Two series of tests are performed, the first in the \num{100}--\SI{500}{\um} subregions of regions B and C and the second in the \SI{500}{\um}--\SI{10}{\cm} subregions of regions B and C.

\subsubsection{\num{100}--\SI{500}{\um} tests}
We perform closure tests in subregions of regions B and C where one lepton is more prompt (\num{20}--\SI{100}{\um}) and the other is more displaced (\num{100}--\SI{500}{\um}). In these closure tests, we estimate the background yield using the simple ABCD method and use the ratio of the actual number of events to the estimated number of events as a measure of nonclosure (and therefore \ada-\adb correlation). With this approach, a ratio of 1 corresponds to closure and negligible correlation while ratios greater than 1 correspond to nonclosure and positive correlation. To understand how the degree of correlation varies with \ad, we perform several closure tests in each sideband while varying the \ad range of the more-prompt lepton and fit the resulting ratios with a first-degree polynomial. We then extrapolate the resulting fit from the closure test regions to SR I to estimate the degree of nonclosure in SR I. We perform identical procedures in regions B and C and then average the resulting extrapolated ratios.

Table \ref{100to500um_tests} shows the average extrapolated ratios for three rounds of closure tests: one in background simulation with the \ztautaull events removed, one in the full background simulation, and one in data. The average extrapolated ratios are always compatible with one in background simulation without \ztautaull events, but they generally increase when the \ztautaull events are included. Furthermore, the average extrapolated ratios from the full background simulation generally describe the average extrapolated ratios in data. From these results, we conclude that within our statistical uncertainties, \ztautaull events are the only meaningful source of correlation and that the degree of correlation observed in data is modeled reasonably well in simulation. We also observe that the variation in the degree of correlation across channels matches our expectations: correlation increases with the number of muons in the final state and is greater in 2017--2018 than 2016 because of the improved $d_0$ resolution made possible by the Phase-1 tracker upgrade (described in Section~\ref{tracker}).

\input{tables/100to500um_tests}

\subsubsection{\SI{500}{\um}--\SI{10}{\cm} tests}
We next perform closure tests in more-displaced subregions of regions B and C where one lepton is more prompt (\num{20}--\SI{100}{\um}) and the other is more displaced (\SI{500}{\um}--\SI{10}{\cm}). We again use the ratio of the actual number of events to the estimated number of events as the measure of nonclosure, but in these tests we expect the ratio to be consistent with one because \ztautaull events do not contribute meaningfully beyond \SI{500}{\um}. Table \ref{500umto10cm_tests} shows that this is indeed the case for background simulation (with and without \ztautaull events) and for data. These results imply that \ada and \adb are uncorrelated beyond \SI{500}{\um}, which means that a simple ABCD procedure will be adequate for estimating the background yields in SRs II, III, and IV.

\input{tables/500umto10cm_tests}

\subsection{ABCD correction and systematic uncertainty}
\label{abcd_correction}
The closure tests of Section~\ref{cr_closure_tests} show that \ada and \adb are frequently positively correlated in the \num{100}--\SI{500}{\um} region but are uncorrelated otherwise. To account for this correlation as well as other possible unforeseen sources of nonclosure, we define a procedure to correct the simple ABCD estimate in SR I and assign a systematic uncertainty to the simple ABCD estimate in all SRs.

\subsubsection{\num{100}--\SI{500}{\um} correction and systematic uncertainty}
Figures~\ref{100to500um_fits_emu}, \ref{100to500um_fits_ee}, and \ref{100to500um_fits_mumu} show the results of the data closure tests in the \Pe\Pgm\, \Pe\Pe, and \Pgm\Pgm\ channels, respectively, in the subregions of regions B and C where one lepton is more prompt (\num{20}--\SI{100}{\um}) and the other is more displaced (\num{100}--\SI{500}{\um}). These plots show the ratio of the actual to the estimated number of events as a function of the prompt lepton \ad. In each plot, the binning of the prompt lepton axis is initially \SI{10}{\um} wide. Starting from most-displaced bin, we test to see if any bin has fewer than 5 events, and if so, we combine it with whichever neighboring bin has fewer events, repeating until all bins have at least 5 events.

In each of the two sidebands, we then fit the resulting ratios with a straight line, where the slope and y-intercept are allowed to vary, and extrapolate the fit to \SI{200}{\um}, which is where we expect the largest contribution from tau lepton decays (see Section~\ref{bg_sources}). \SI{200}{\um} also happens to be approximately the center-of-mass of the \num{100}--\SI{500}{\um} bin in background simulation. We average the two extrapolated ratios and derive a correction and systematic uncertainty from this average extrapolated ratio.

\input{figures/bg/100to500um_fits}

If the average extrapolated ratio is $>1.0$, we take the central value as a multiplicative correction to the background estimate and the uncertainty in the average as a systematic uncertainty in the background estimate. In this case, we also vary the \SI{200}{\um} extrapolation point by $\pm\SI{50}{\um}$ (the approximate width of the peak in the tau lepton contribution as a function of \ad). We apply the difference from this variation in extrapolation point as an additional systematic uncertainty in the background estimate. If the average is $\leq 1.0$, we set the correction equal to $1.0$ and use the uncertainty in the average as a symmetric systematic uncertainty about $1.0$. Table~\ref{100to500um_estimates} shows the resulting correction factors along with the uncorrected and corrected SR I background estimate.

\input{tables/100to500um_estimates}

\subsubsection{\SI{500}{\um}--\SI{10}{\cm} systematic uncertainty}
In the \SI{500}{\um}--\SI{10}{\cm} region, we derive a systematic uncertainty in the background estimate from the data closure tests shown in Section~\ref{cr_closure_tests}. We take the largest deviation from \num{1.0} that occurs in the ratio of the actual to the estimated number of events plus its uncertainty, in either of the two closure tests that correspond to a given SR, as a systematic uncertainty. This is a conservative approach that produces a large systematic uncertainty in the small background yields that we predict in these regions. Table \ref{500umto10cm_estimates} shows the systematic uncertainty and the predicted number of events in SRs II, III, and IV.

\input{tables/500umto10cm_estimates}

\subsection{Testing full background estimation procedure}

Having defined the full background estimation procedure and seen that the \ada-\adb correlation observed in data is also present in simulated background events, we now perform a final closure test of the full background estimation method using simulated background events in SRs I--IV.

Table~\ref{sr_closure_tests} shows the estimated and actual number of simulated background events in SRs I--IV. The listed estimates include all corrections and statistical and systematic uncertainties as discussed in \ref{abcd_correction}. The uncertainties in the actual values are purely statistical. The general agreement between estimated and actual yields leads us to conclude that the background estimation procedure is valid and the assigned systematic uncertainties are sufficient to cover any potential sources of nonclosure that we have not explicitly considered.

\input{tables/sr_closure_tests}

\subsection{Additional background checks}
\label{additional_bg_checks}
We perform a few additional studies to check for other potential sources of background. We find that their SR contributions are either negligible or already covered by the background estimation method described above.

\subsubsection{Material interactions}
In order to further study the material interactions, we invert the preselection criterion that rejects good vertices in the material. In data, we find seven events, across all channels and years, that pass the preselection with this inverted criterion. As shown in Table~\ref{material_interaction_evts}, three of these events are in the prompt control region and four are in region B or region C. The lepton vertices in these events coincide with the material as we expect: two are in the beampipe, one is in the pixel detector inner shield, and four are in the first layer of the pixel detector. Even with the material interaction veto inverted, we find no SR events resulting from material interactions and therefore conclude that material interactions are not a significant background after the full selection is applied.

\input{tables/material_interaction_evts}

\subsubsection{Cosmic-ray muons}
To estimate the SR contribution of cosmic-ray muons, we perform a study in which we invert the $\Delta t$ and $\cos{\alpha}$ criteria in the \Pgm\Pgm\ preselection and check how many events are in the SRs. We find three data events with the criteria inverted (one event per year, all in SR IV). Next, we use \texttt{NoBPTX} data, which is dominated by cosmic-ray muon events, to estimate the efficiency for cosmic-ray muons to pass the $\Delta t$ and $\cos{(\alpha)}$ criteria after passing the rest of the \Pgm\Pgm\ preselection criteria. While \num{3736} \texttt{NoBPTX} data events pass the preselection criteria with the $\Delta t$ and $\cos{(\alpha)}$ criteria removed, zero \texttt{NoBPTX} data events pass the full preselection. To conservatively estimate the efficiency, we fluctuate the number of passing events up to 1 and find an efficiency of $1/3736$. We therefore find the approximate upper bound on the SR contribution of cosmic-ray muons to be $3\times\frac{1}{3736}=0.0008$, which is negligible compared to the background estimation in each SR.

\subsubsection{Heavy-flavor mesons}
We perform two studies to estimate an upper limit on the SR contribution of leptons from heavy-flavor mesons. First, we estimate SR yields with a simple ABCD method in 2018 \Pgm\Pgm\ preselection data while additionally requiring at least one medium CSVv2 \PQb-tagged jet~\cite{bjet_identification}. The test is performed in the \Pgm\Pgm\ channel because it contains the smallest relative SR contribution from mismeasurements and should therefore be most sensitive to heavy flavor. As shown in Table~\ref{abcd_hf_data}, the background estimates are about an order of magnitude smaller than when no \PQb-tagged jet is required in our usual preselection.

\input{tables/abcd_hf_data}

Next, we look at 2018 data and simulated QCD multijet events that pass the \Pgm\Pgm\ preselection with the isolation criterion inverted. These samples are dominated by muons from B meson decays, and the QCD simulation describes the data well in the region outside of the \cPZ\ boson peak, as shown in Fig.~\ref{mumu_inv_mass_inverted_iso}. We use this QCD multijet sample to test the heavy-flavor background in two ways. First, we perform a simple ABCD estimate in the simulated QCD multijet events to check for \ada-\adb correlation. As shown in Table~\ref{abcd_hf_mc}, we find no evidence of correlation, which indicates that the background estimation already accounts for the heavy-flavor background. Second, we estimate the approximate heavy-flavor background in the SRs by taking the ratio of SR to prompt control region events in QCD multijet simulation from the anti-isolated region and the normalization from the number of simulated QCD multijet events that pass the \Pgm\Pgm\ preselection. Using this approach, we estimate that the heavy-flavor background to be $0.06^{+0.13}_{-0.05}$ events in SR I and $0.0015^{+0.0034}_{-0.0012}$ events in SR IV, which is small relative to the nominal prediction shown in the first row of Table~\ref{abcd_hf_data}.

\input{figures/bg/mumu_inv_mass_inverted_iso}
\input{tables/abcd_hf_mc}

We therefore conclude that the heavy-flavor SR contribution is small and already accounted for in our background estimates.

\subsubsection{Low-mass SM hadrons}
To estimate an upper limit on the SR contribution of leptons from decays of low-mass SM hadrons, we examine 2018 data and QCD multijet simulation in the \Pgm\Pgm\ channel with both the muon isolation and the $\DR$ requirements inverted. As shown in Fig.~\ref{mumu_inv_mass_inverted_iso_lo}, this region is dominated by low-mass muon pairs, with clear J/$\psi$, $\psi^\prime$, and $\Upsilon$ mass peaks. Many of these leptons are displaced, especially those in the J/$\psi$ mass range. To estimate the fraction of such leptons that will be displaced, we take the ratio of SR to prompt control region events of SM hadrons that decay to leptons from data in this region.

\input{figures/bg/mumu_inv_mass_inverted_iso_lo}

Even though the inverted-isolation region is dominated by low-mass muon pairs, the only QCD multijet simulation event that survives the 2018 \Pgm\Pgm\ preselection has a di-muon invariant mass of approximately 300\GeV. Furthermore, the muons are not near each other in the $\eta$-$\phi$ plane ($\DR\approx3$), which is inconsistent with the low-mass SM hadron events that dominate the region with the inverted isolation and $\DR$ criteria. To find a normalization from which to estimate the low-mass SM hadron SR contribution, we therefore turn to the inverted-isolation sample used above in the heavy-flavor meson cross check. In this sample, the ratio of events with $\DR<0.5$ to events with $2.8<\DR<3.2$ is about $0.1$. We find $0.2$ QCD multijet simulated events that pass the nominal preselection, and so we estimate that of the events passing the 2018 \Pgm\Pgm\ preselection, about $0.02$ contain pairs of muons produced in low-mass SM hadron decays. We estimate the SR contributions using this preselection normalization and the ratio of SR to prompt control region events from the sample of SM hadrons that decay to leptons in data. We find this contribution is less than $0.006^{+0.013}_{-0.005}$ events in SR I and less than $0.001^{+0.002}_{-0.001}$ events in SR IV, which, if compared with the nominal prediction shown in the first row of Table~\ref{mumu_inv_mass_inverted_iso}, are respectively negligible and easily covered by the \SI{140}{\percent} systematic uncertainty already applied to the background prediction in this region.

\pagebreak